---
title: "Exercise 8"
author: "Saverio PIetro Capra"
date: "2025-01-23"
output: html_document
---

```{r pressure, echo=TRUE}
library(datasets)
data(iris)
```

## Example 1.12

In this example we display several versions of a scatterplot of the iris sepal width and sepal length data, using the `ggplot2` library contained in the `tidyverse` package.

```{r pressure, echo=TRUE}
ggplot(data = iris, aes(x=Sepal.Length, y = Sepal.Width)) + geom_point()
```

Here we have, respectively specified:

-   The data we're going to use: "iris"

-   A mapping for our variables `Sepal.length` and `Sepal.Width` to a visual object (`geom`)

Now, in order to display different colors and symbols for the 3 different species of iris, we can write the following code:

```{r pressure, echo=TRUE}
ggplot(data = iris, aes(x=Sepal.Length, y = Sepal.Width, 
                        color = Species, shape = Species)) + geom_point(size = 2)
```

## Example 1.13

Now, let's use the `ggplot2` library to display parallel boxplots and violin plots for the iris sepal length measurement by species.

```{r pressure, echo=FALSE}
ggplot(iris, aes(Species, Sepal.Length))+geom_boxplot()
ggplot(iris, aes(Species, Sepal.Length)) + geom_violin()
```

If we want to display horizontal plots, we just need to add `coord_flip`:

```{r pressure, echo=FALSE}
ggplot(iris, aes(Species, Sepal.Length))+geom_boxplot()+coord_flip()
ggplot(iris, aes(Species, Sepal.Length)) + geom_violin()+coord_flip()
```

## Example 1.14

Now, we refer to the `mpg` data contained in `ggplot2`. The data records fuel economy data from 1999 and 2008 for 38 models of cars.

Our goal is to plot highway mpg (`hwy`) as a function of engine size (displacement `displ`) for each `class` of vehicle, and display all of these plots in an array.

```{r pressure, echo=FALSE}
ggplot(mpg, aes(displ, hwy))+
  geom_point() +
  facet_wrap(~ class)
```
